---
title: "flowers-figures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flowers-figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE, 
  comment = "#>"
)
library(matRiks)
```


This vignette illustrates all the flower-like figures available in the `matRiks` package. To obtain the single figures to use for concatenating the figures, use the prefix `s_` before the command of the figure. For instance, to obtain a single lily, use the command `s_lily()`. 

The difference between `lily()` and `miley()` lies in how the two flowers are composed. `lily()` is a `compose2`, since it is composed of a vertical and an horizontal eight. Conversely, `miley()` is a `compose4`, since it is composed of 4 petals. 

::::{style="display: flex;"}
::: {}
```{r}
draw(up_petal(), main = "up_petal()")
```

```{r}
draw(down_petal(), main = "down_petal()")
```

```{r}
draw(lily(), main = "lily()")
```

:::


::: {}
```{r}
draw(right_petal(), main = "right_petal()")
```

```{r}
draw(left_petal(), main = "left_petal()")
```


```{r}
draw(miley(), main = "miley()")
```


:::

::::
